Output Summary

### 2021-12-11 03-post-process/output-plots.Rmd
Better handling of years to plot in all fit plots

  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,3,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,4,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 4), main = TeX("$Age\\,3\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,5,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 5), main = TeX("$Age\\,4\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,6,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 6), main = TeX("$Age\\,5\\,(NOR)$"))
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Carcasses")
}

# for fits to each age, aggregated across origins
carc_comp_fit_plot_age = function(j) {
  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[.+,3,pop]$", pop = j)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"))
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}

# for fits to each origin, aggregated across ages
carc_comp_fit_plot_origin = function(j) {
  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_origin[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_origin_obs[observable,,j], 1), main = TeX("$NOR$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_origin[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_origin_obs[observable,,j], 2), main = TeX("$HOR$"))
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}

>>>>

  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 4), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 5), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 6), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Carcasses")
}

# for fits to each age, aggregated across origins
carc_comp_fit_plot_age = function(j) {
  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), yrs = all_yrs[ts_yrs])
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}

# for fits to each origin, aggregated across ages
carc_comp_fit_plot_origin = function(j) {
  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_origin_obs[observable,,j], 1), main = TeX("$NOR$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_origin_obs[observable,,j], 2), main = TeX("$HOR$"), yrs = all_yrs[ts_yrs])
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}
